A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-10 4_method.tex
remove old figures

\begin{figure}
% from /home/t.kuipers/Documents/PhD/Variable_Width_project/pathplanning preliminaries/straight_skeleton_vs_medial_axis.svg
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/example_straight_skeleton.pdf}
\caption{Straight skeleton}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/example_medial_axis.pdf}
\caption{Medial axis}
\end{subfigure}
\caption{Example polygon middle analysis thingies. Difference is colored.}
\label{medial_axis_vs_straight_skeleton}
\end{figure}

\begin{figure}
\begin{subfigure}{0.24\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
\caption{MAT}
\end{subfigure}
\begin{subfigure}{0.24\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/Voronoi_example.pdf}
\caption{Voronoi}
\end{subfigure}
\begin{subfigure}{0.24\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
\caption{gMAT}
\end{subfigure}
\begin{subfigure}{0.24\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example_labeling.pdf}
\caption{Quads}
\end{subfigure}
\caption{Grounded medial axis transform. Dark red are linear segments,  bright red are parabolic segments with high curvature, parabola segments with low curvature are purple. The labelings of areas show that the gMAT divides the area into quads and triangles and that the medial axis divides the area into sub-areas for each outline polygon.}
\label{gmat}
\end{figure}

@@

However, instead of removing bones from the Voronoi diagram we will introduce more bones such that the skeleton discretizes the boundary shape into quads within which the $R$ can be interpolated linearly.
We call the resulting skeletonization the \emph{Voronoi Quadrangulation} (VQ).
The VQ greatly simplifies the processing required downstream in our framework.

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{sources/method/voronoi_MAT.png}
\caption{From \citeauthor{lee1982medial} \cite{lee1982medial}}
\label{voronoi_MAT}
\end{figure}

@@

\subsubsection{Significance measure}\label{sec:significance_measure}
\Cref{rounded_dist_measures}
Places where the naive concentric toolpathing strategy would create large underfilling and overfilling areas are locations which intuitively look like `the center' of the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\widehat{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$. \cite{attali1996modeling}
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill.
Contrary to related literature we will \emph{keep} the insignificant regions of the skeleton.
Our framework will employ a different toolpathing strategy to prevent overfill and underfill areas if they would be so large that $\alpha > \alpha_\text{max}$.

@@

\subsubsection{Transitioning}

\begin{figure}
\centering
\includegraphics[width=.6\columnwidth]{sources/method/rounded_dist_measures.jpg}
\caption{MAT distance measures at existing joints can be non-integer multiples of bead width.}
\label{rounded_dist_measures}
\end{figure}

See \cref{rounded_dist_measures}.

In order to prevent discontinuities in the toolpaths around locations $p$ where $\exists n : R(p) = b^{-1}(n)$ (see \cref{transition_location}), we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
The transition will be placed so as to overlap the locations of $b^{-1}(n)$.

>>>>

\begin{figure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
\caption{MAT}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/Voronoi_example.pdf}
\caption{Limited VD}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
\caption{VQ}
\end{subfigure}
\caption{
Relation between the medial axis, the limited Voronoi Diagram and the Voronoi quadrangulation: MAT $\subset$ Limited VD $\subset$ VQ.
Significant parts of the skeleton are visualized in shades of red, insignificant regions in grey and blue.
}
\label{skeletonization_comparison}
\end{figure}

@@

However, instead of removing bones from the Voronoi diagram we will introduce more bones such that the skeleton discretizes the boundary shape into quads within which the $R$ can be interpolated linearly.
We call the resulting skeletonization the \emph{Voronoi Quadrangulation} (VQ).
See \cref{skeletonization_comparison}.
The VQ greatly simplifies the processing required downstream in our framework.

@@

@@

\subsubsection{Significance measure}\label{sec:significance_measure}
Places where the naive concentric toolpathing strategy would create large underfilling and overfilling areas are locations which intuitively look like `the center' of the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\widehat{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$. \cite{attali1996modeling}
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill.
Contrary to related literature we will \emph{keep} the insignificant regions of the skeleton.
Our framework will employ a different toolpathing strategy to prevent overfill and underfill areas if they would be so large that $\alpha > \alpha_\text{max}$.

@@

\subsubsection{Transitioning}
In order to prevent discontinuities in the toolpaths around locations $p$ where $\exists n : R(p) = b^{-1}(n)$ (see \cref{transition_location}), we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
The transition will be placed so as to overlap the locations of $b^{-1}(n)$.
